Analysis paper

### 2021-06-19 analysis/analysis.Rmd
update plots

@@

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "mean WIS", x = "Forecast horizon")

# median performance
p_median <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "median WIS", x = "Forecast horizon") + 
  theme_minimal()

ggsave(here("analysis", "plots", "aggregate-performance-median.png"))

# sd of performance
p_wis_sd <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "WIS - standard deviation", x = "Forecast horizon") + 
  theme_minimal()

ggsave(here("analysis", "plots", "aggregate-performance-wis-sd.png"))

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "sharpness", x = "Forecast horizon") + 
  theme_minimal()

ggsave(here("analysis", "plots", "aggregate-performance-sharpness.png"))

# absolute error of performance
p_aem <- scores %>%
  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Absolute error", x = "Forecast horizon") + 
  theme_minimal()

ggsave(here("analysis", "plots", "aggregate-performance-aem.png"))

# bias
p_bias <- scores %>%
  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Bias", x = "Forecast horizon") + 
  theme_minimal()

ggsave(here("analysis", "plots", "aggregate-performance-bias.png"))

@@

ggsave(here("analysis", "plots", "aggregate-performance-coverage50.png"))

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  geom_hline(yintercept = 0.90, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "empirical coverage", x = "Forecast horizon") + 
  expand_limits(y=c(0, 1)) + 
  scale_y_continuous(labels = scales::percent)

ggsave(here("analysis", "plots", "aggregate-performance-coverage90.png"))

@@

ggsave(here("analysis", "plots", "aggregate-performance-all.png"), 
       height = 12, width = 10)

>>>>

# colcases <- few_pal()(4)[-1]
# coldeaths <- few_pal()(4)

@@

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "mean WIS", x = NULL)

# ggsave(here("analysis", "plots", "aggregate-performance-mean.png"))

# median performance
p_median <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "median WIS", x = NULL) + 
  theme_minimal()

# ggsave(here("analysis", "plots", "aggregate-performance-median.png"))

# sd of performance
p_wis_sd <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "WIS - sd", x = NULL) + 
  theme_minimal()

# ggsave(here("analysis", "plots", "aggregate-performance-wis-sd.png"))

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "sharpness", x = NULL) + 
  theme_minimal()

# ggsave(here("analysis", "plots", "aggregate-performance-sharpness.png"))

# absolute error of performance
p_aem <- scores %>%
  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Absolute error", x = NULL) + 
  theme_minimal()

# ggsave(here("analysis", "plots", "aggregate-performance-aem.png"))

# bias
p_bias <- scores %>%
  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  expand_limits(y=c(-0.2, 0.2)) + 
  labs(y = "Bias", x = NULL) + 
  theme_minimal()

# ggsave(here("analysis", "plots", "aggregate-performance-bias.png"))

@@

# ggsave(here("analysis", "plots", "aggregate-performance-coverage50.png"))

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  geom_hline(yintercept = 0.90, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Empirical coverage", x = "Forecast horizon") + 
  expand_limits(y=c(0, 1)) + 
  scale_y_continuous(labels = scales::percent)

# ggsave(here("analysis", "plots", "aggregate-performance-coverage90.png"))

@@

ggsave(here("analysis", "plots", "aggregate-performance-all.png"), 
       height = 9.1, width = 10)
